---
title: "MRP"
author: "Flavio Morelli"
date: "4/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rstanarm)
options(mc.cores = parallel::detectCores())
```

# MRP

## Fake data for MRP

-   Yes / No dependent variable

-   categories: sex, age, ethnicity

```{r }
J <-  c(2, 4, 4)
poststrat <-  as.data.frame(array(data = NA, 
                                dim = c(prod(J), 
                                dimnames = length(J) + 1)))
colnames(poststrat) <-  c("sex", "age", "eth", "N")
head(poststrat)
```

Populate the table with the combinations of the different categories

```{r}
count <- 0
for(i1 in 1:J[1]){
  for(i2 in 1:J[2]){
    for(i3 in 1:J[3]){
      count <- count + 1
      poststrat[count, 1:3] <- c(i1, i2, i3)
    }
  }
}
head(poststrat)
```

Create numbers for populations of the cells

```{r}
p_sex <- c(0.52, 0.48)
p_age <-c(0.2, 0.25, 0.3, 0.25)
p_eth <- c(0.7, 0.1, 0.1, 0.1)
for(j in 1:nrow(poststrat)){
  poststrat$N[j] <-  250e6 * p_sex[poststrat[j, 1]] *       
                      p_age[poststrat[j, 2]] *
                      p_eth[poststrat[j, 3]]
}
head(poststrat)
```

We hyposthesize a nonresponse pattern in which women, older people and whites are more likley to respond than men, younger people and minorities

```{r}
p_response_baseline <- 0.1
p_response_sex <- c(1, 0.8)
p_response_age <- c(1, 1.2, 1.6, 2.5)
p_response_eth <- c(1, 0.8, 0.7, 0.6)
p_response <- rep(NA, prod(J))
for(j in 1:nrow(poststrat)){
  p_response[j] <- p_response_baseline * 
    p_response_sex[poststrat[j, 1]] *
    p_response_age[poststrat[j, 2]] *
    p_response_eth[poststrat[j, 3]]
}
p_response
```

Sample from population with assumed nonresponse probabilities

```{r}
n <- 1000
people <- sample(nrow(poststrat), n, 
                 replace = TRUE, prob=poststrat$N*p_response)
head(people)
```

Calculate sample size for each cell

```{r}
n_cell <-  rep(NA, nrow(poststrat))
for(j in 1:nrow(poststrat)){
  n_cell[j] <- sum(people==j)
}
head(n_cell)
```

Check deviations between samples and population

```{r}
print(cbind(poststrat, n_cell/n, poststrat$N/sum(poststrat$N)))
```

Model response probability with a logistic regression

```{r}
coef_intercept <- 0.6
coef_sex <- c(0, -0.2)
coef_age <- c(0, -0.2, -0.3, -0.4)
coef_eth <- c(0, 0.6, 0.3, 0.3)

prob_yes <- rep(NA, nrow(poststrat))
for(j in 1:nrow(poststrat)){
  prob_yes[j] <- boot::inv.logit(coef_intercept +
                                   coef_sex[poststrat[j, 1]] +
                                   coef_age[poststrat[j, 2]] +
                                   coef_eth[poststrat[j, 3]])
}
prob_yes
```

Simulate fake data

```{r}
y <- rbinom(n, 1, prob_yes[people])
head(y)
```

Performing regression

```{r}
sex <- poststrat[people, 1]
age <- poststrat[people, 2]
eth <- poststrat[people, 3]
fake <- data.frame(y, sex, age, eth)
head(fake)
```

```{r}
fit <- stan_glm(y ~ factor(sex) + factor(age) + factor(eth),
                family=binomial(link="logit"), data=fake)
```

```{r}
print(fit)
```

Generate predictions for the proportion of yes predictions for each cello

```{r}
pred_sim <- posterior_epred(fit, newdata=as.data.frame(poststrat))
pred_est <- colMeans(pred_sim)
print(cbind(poststrat, prob_yes, pred_est))
```

Finally, poststratify:

```{r}
poststrat_est <- sum(poststrat$N*pred_est)/ sum(poststrat$N)
round(poststrat_est, 3)
```

```{r}
mean(y)
```

Get uncertainty

```{r}
poststrat_sim <- pred_sim %*% poststrat$N / sum(poststrat$N)
round(c(mean(poststrat_sim), sd(poststrat_sim)), 3)
```
